Iterative Monomorphisation

### 2025-02-19 iterative_monomorphisation.tex
shorten

Each bound of the monomorphisation process presents a tradeoff: a higher bound allows for a more exhaustive instantiations of type variables at the cost of taking more time. Ideally, all possible combinations of values for all bounds could be exhaustively tested to find the best compromise between completeness and speed. Given the number of bounds, however, this is unfeasible. Instead, we group closely related bounds together and test combinations of values for the bounds in these groups. Once we find the best performing set of values for a group of bounds, we assign these values to the corresponding bounds as we begin the search for the next group. If several groups of bounds result in the same number of proved problems, the most constraining bound values are selected. Winning entries are shown in bold in Tables \ref{mono_ty_args} to \ref{e_settings}.

@@

%The substitution generation phase occurs once all type arguments have been generated. The bounds limiting the number of new substitutions and the number of monomorphising substitutions per formula are directly related through the role they play in the construction of monomorphising substitutions. The substitution ordering heuristic has a significant impact on monomorphising substitution generation. The ``age'' ordering of substitution orders substitutions generated in earlier iterations are ordered first. The ``random'' ordering randomly shuffles substitutions. Finally, the ``separation'' ordering separates the substitutions into different sets depending on which iteration they were generated in and generates monomorphising substitutions from each of these sets independently. Table \ref{subst_gen_table} shows that the values of bounds limiting the number of substitutions generated has very little impact on overall performance contrary to the ordering heuristic.
The substitution generation phase occurs once all type arguments have been generated. The bound limiting the number of monomorphising substitutions per formula is directly related to the ordering which dictates how such monomorphising substitutions are generated. The substitution ordering heuristic has a substantial impact on monomorphising substitution generation. The `age' ordering of substitution orders substitutions generated in earlier iterations are ordered first. The `random' ordering randomly shuffles substitutions. Finally, the `separation' ordering separates the substitutions into groups of substitutions generated in the same iteration and generates monomorphising substitutions from each of these groups independently. Table \ref{subst_gen_table} shows that the values of bounds limiting the number of monomorphising substitutions only seems to affect performance when the `separation' heuristic is used.
% TODO find a better term than "separation heuristic" maybe separation ?

>>>>

Each bound of the monomorphisation process presents a tradeoff: a higher bound allows for a more exhaustive instantiations of type variables but takes more time. Ideally, all possible combinations of values for all bounds could be exhaustively tested to find the best compromise between completeness and speed. Given the number of bounds, however, this is unfeasible. Instead, we group closely related bounds together and test combinations of values for the bounds in these groups. Once we find the best performing set of values for a group, we assign these values to the corresponding bounds as we begin the search for the next group. If several groups result in the same number of proved problems, we select the most constraining values. Winning entries are shown in bold in Tables \ref{mono_ty_args} to \ref{e_settings}.

@@

%The substitution generation phase occurs once all type arguments have been generated. The bounds limiting the number of new substitutions and the number of monomorphising substitutions per formula are directly related through the role they play in the construction of monomorphising substitutions. The substitution ordering heuristic has a significant impact on monomorphising substitution generation. The ``age'' ordering of substitution orders substitutions generated in earlier iterations are ordered first. The ``random'' ordering randomly shuffles substitutions. Finally, the ``separation'' ordering separates the substitutions into different sets depending on which iteration they were generated in and generates monomorphising substitutions from each of these sets independently. Table \ref{subst_gen_table} shows that the values of bounds limiting the number of substitutions generated has very little impact on overall performance contrary to the ordering heuristic.
The substitution generation phase occurs once all type arguments have been generated. The bound limiting the number of monomorphising substitutions per formula is directly related to the ordering which dictates how such monomorphising substitutions are generated. The %substitution ordering
heuristic greatly affects monomorphising substitution generation. The `age' ordering of substitution orders substitutions generated in earlier iterations first. The `random' ordering randomly shuffles substitutions. Finally, the `separation' ordering separates the substitutions into groups of substitutions generated in the same iteration and generates monomorphising substitutions from each of these groups independently. Table \ref{subst_gen_table} shows that the values of bounds limiting the number of monomorphising substitutions only seems to affect performance when the `separation' heuristic is used.
% TODO find a better term than "separation heuristic" maybe separation ?
